
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Akansha Kumari} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} {8050208662}
    $|$
    \faAt \hspace{.5pt} \href{mailto:akskum110@gmail.com}{akskum110@gmail.com}
    $|$
    
    $|$
    
    $|$
    
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
{Atria Institute of Technology
}{Bengaluru, Karnataka}
{Bachelor of Engineering in Information Science and Engineering;   \textbf{CGPA: 8.0/10.0}}{September. 2021 \textbf{--} July 2025}

\resumeSubheading
{Omega Mission School 
}{Patna, Bihar}
{CLASS 12 in science stream;   \textbf{CGPA: 79\%}}{2020 \textbf{--} 2021}

\resumeSubheading
{Omega Mission School 
}{Patna, Bihar}
{CLASS 10 in ;   \textbf{CGPA: 78.4\%}}{2018 \textbf{--} 2019}


  \resumeSubHeadingListEnd


%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
      {Compsoft Technologies}{Bengaluru}
      {UI/UX Design INTERN}{November.2023 \textbf{--} December.2023}
      \resumeItemListStart
      \resumeItem{Created user-centric Car Rental App with seamless UI/UX, leveraging Figma for design and prototyping}\resumeItem{Created clean and responsive UI layouts using Figma.}\resumeItem{Built interactive prototypes to demonstrate user flows and functionality.}
        \resumeItemListEnd

\resumeSubheading
      {Karunada Technologies}{Bengaluru}
      {Python and Machine Learning}{April, 2022 \textbf{--} May.2022}
      \resumeItemListStart
      \resumeItem{Gained comprehensive knowledge in Python programming, including data structures, algorithms, and object-oriented programming.}\resumeItem{
Applied Object-Oriented Programming (OOPs) concepts to structure code efficiently.

}\resumeItem{Explored and implemented basic machine learning models using Python libraries.}
        \resumeItemListEnd

\resumeSubheading
      {Rooman Technologies }{Bengaluru, INDIA}
      {AI DEVOPS Intern    }{September 2024 \textbf{--} January 2025}
      \resumeItemListStart
      \resumeItem{•Gained foundational knowledge of DevOps practices, including CI/CD pipelines and Docker. Automated software workflows and containerized AI models for deployment. Collaborated effectively in team settings, engaging in peer code reviews. Completed mini-project involving AI model deployment using Flask and Docker.
}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeProjectHeading
{\textbf{Firesphere 360-Autonomous Rotating Fire Extinguisher} $|$ \underline{\emph{\href{}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Developed an IoT-powered fire extinguisher capable of autonomously detecting and extinguishing fires.}\resumeItem{Integrated a mobile app for remote control, providing real-time monitoring and manual intervention.}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{ UI Design for E-Commerce Website} $|$ \underline{\emph{\href{}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Designed responsive UI using modern UI/UX principles. }\resumeItem{Created wireframes and prototypes with Figma/Adobe XD.}\resumeItem{Focused on mobile-first design and user-friendly navigation.}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{Improving deployment speed and reducing production issues with devops practices} $|$ \underline{\emph{\href{}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Implemented DevOps methodologies to streamline the software delivery lifecycle. }\resumeItem{Automated build, test, and deployment using CI/CD tools (Jenkins, GitHub Actions). }\resumeItem{Improved deployment speed and reduced post-release bugs and downtime.}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeItemListStart
  \resumeItem{•Winner of Social Connect and Responsibilities (SCR) Initiative
  ecognized for outstanding contribution and impactful project work under the Social Connect and Responsibilities Rprogram, demonstrating social awareness, innovation, and teamwork.
 }
  \resumeItemListEnd


%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

  
    \textbf{Languages:}{  HTML/CSS, MYSQL} \ \vspace{3pt}

    \textbf{Technical Skills:}{ Basic of Cloud Computing.
UI/UX design.
DEVOPS tool.
} \ \vspace{3pt}

    \textbf{ Tools & Technologies:}{ Microsoft Excel} \ \vspace{3pt}

}}
\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
