
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


%---------- FONT OPTIONS ----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}



%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Akansha kumari} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} {8050208662}
    $|$
    \faAt \hspace{.5pt} \href{mailto:akskum110@gmail.com}{akskum110@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/akansha-kumari-9852b1282?utm_source=share&utm_campaign=share_via&utm_content=profile&utm_medium=android_app}{LinkedIn}
    $|$
    
    $|$
    
\end{center}



%----------- EDUCATION -----------

\section{Education}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
{Atria Institute of Technology
}{bangalore, india}
{Bachelor of Engineering (B.E.)  in Information Science and Engineering;   \textbf{CGPA: 8.0/10.0}}{oct 2021 \textbf{--} may 2025}

\resumeSubheading
{Omega Mission School 
}{Patna, Bihar}
{Senior Secondary (12th Grade) in science stream;   \textbf{CGPA: 79\%}}{2019 \textbf{--} 2021}

\resumeSubheading
{Omega Mission School 
}{Patna, Bihar}
{Secondary (10th Grade) in ;   \textbf{CGPA: 78.4\%}}{2018 \textbf{--} 2019}


  \resumeSubHeadingListEnd


%----------- EXPERIENCE -----------

\section{Experience}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeSubheading
      {Rooman Technologies }{Bengaluru, INDIA}
      {AI DEVOPS Intern  }{September 2024 \textbf{--} January 2025}
      \resumeItemListStart
      \resumeItem{Gained foundational knowledge of DevOps practices, including CI/CD pipelines and Docker.
Automated software workflows and containerized AI models for deployment.
Collaborated effectively in team settings, engaging in peer code reviews.
Completed mini-project involving AI model deployment using Flask and Docker.

}
        \resumeItemListEnd

\resumeSubheading
      {Varcons Technologies }{Bengaluru, INDIA}
      {UI/UX design Intern}{October 2023  \textbf{--}  December 2023}
      \resumeItemListStart
      \resumeItem{Acquired practical knowledge of UI/UX design principles, user-centered design, wireframing, and prototyping.
Designed user interfaces for real-world projects utilizing Figma and Adobe XD.

}
        \resumeItemListEnd

\resumeSubheading
      {Karunadu Technologies}{Bengaluru, INDIA}
      {python and Machine Learning intern}{October 2022  \textbf{--}  November 2022}
      \resumeItemListStart
      \resumeItem{Executed real-world machine learning project utilizing Python and libraries like Pandas and NumPy.
Collected, cleaned, and analyzed datasets in preparation for model training.
Constructed and trained ML models employing classification and regression algorithms such as Decision Tree and Random Forest.
}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- PROJECTS -----------

\section{Projects}
  \vspace{3pt}
  \resumeSubHeadingListStart

  
\resumeProjectHeading
{\textbf{Improving deployment speed and reducing production issues with devops practices} $|$ \underline{\emph{\href{}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Implemented DevOps methodologies to streamline the software delivery lifecycle.

Automated build, test, and deployment using CI/CD tools (Jenkins, GitHub Actions).

Used Docker and Kubernetes for containerization and orchestration.

Set up monitoring and alerting with Prometheus and Grafana.

Improved deployment speed and reduced post-release bugs and downtime.

}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{ UI Design for E-Commerce Website} $|$ \underline{\emph{\href{}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Designed responsive UI using modern UI/UX principles.

Created wireframes and prototypes with Figma/Adobe XD.

Built frontend with HTML, CSS, JavaScript (and React/Angular/Vue if applicable).

Focused on mobile-first design and user-friendly navigation.

Collaborated with stakeholders to ensure brand consistency and optimize user engagement.

}
        \resumeItemListEnd

\resumeProjectHeading
{\textbf{Firesphere 360: Autonomous fire extinguisher} $|$ \underline{\emph{\href{}{GitHub}}} } {}
      \resumeItemListStart
      \resumeItem{Developed an intelligent, 360-degree autonomous fire extinguishing system designed to detect and suppress fires in real-time. Integrated sensors (e.g., flame, smoke, temperature) for accurate fire detection and used microcontrollers (e.g., Arduino/Raspberry Pi) to control the response mechanism. Designed a rotating base for 360° coverage and automated nozzle targeting. Ensured fast response time and efficient suppression with minimal human intervention. Aimed at enhancing safety in industrial and residential environments.}
        \resumeItemListEnd


  \resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeItemListStart
  \resumeItem{Winner – Social Connect and Responsibilities (SCR) Initiative

Recognized for outstanding contribution and impactful project work under the Social Connect and Responsibilities program, demonstrating social awareness, innovation, and teamwork.

 }
  \resumeItemListEnd


%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

  
    \textbf{:}{ Cloud computing expertise
UI/UX design
Software development and DevOps
Collaboration and teamwork

Machine learning and data analysis
Adaptability and quick learning
Microsoft Excel
} \ \vspace{3pt}

}}
\resumeSubHeadingListEnd



%----------- Profiles -----------

\section{Profiles}
  \vspace{2pt}
  \resumeItemListStart
  \resumeItem{\underline{\href{https://www.linkedin.com/in/akansha-kumari-9852b1282?utm_source=share&utm_campaign=share_via&utm_content=profile&utm_medium=android_app}{linkdin}}}
  \resumeItemListEnd

%-------------------------------------------
\end{document}
